---
title: "Trait Anxiety and State Inference"
author: "Ondrej Zika"
date: "1/10/2021"
output: html_document
---

## Preparatory steps
- identify root folder
- restore computational environment from $ROOT/renv.lock

```{r setup, include=FALSE}
options(warn=-1)
if (!require("pacman")) install.packages("pacman")
pacman::p_load("renv", "here", "knitr")

knitr::opts_chunk$set(echo = TRUE)

here::i_am(".r_root_folder")
here::here()

renv::restore(project=here::here())
#renv::snapshot()
dir.create(here::here("output/figures/"))

```

## Load packages
```{r}
#library(PupillometryR)
required_packages = c("PupillometryR","ggplot2", "Jmisc", "sjmisc", "plyr", "lme4", "lmerTest", "emmeans", "tidyr", "dplyr", "ggpubr", "purrr", "broom",  "plotrix", "VGAM", "reshape2")
pacman::p_load(char = required_packages)
source(here::here("utils/r_functions.R"))
```

## Load additional tools
```{r}
# load color palettes
pal <- get_colors("ond2")
pal2 <- get_colors("ond")
pal3 <- get_colors("ukr")

plot(NULL, xlim=c(0,length(pal2)), ylim=c(0,1), 
    xlab="", ylab="", xaxt="n", yaxt="n")
rect(0:(length(pal)-1), 0.7, 1:length(pal), 0.9, col=pal)
rect(0:(length(pal2)-1), 0.4, 1:length(pal2), 0.6, col=pal2)
rect(0:(length(pal3)-1), 0.1, 1:length(pal3), 0.3, col=pal3)

```

## 1. Analysis of ratings - stable cues
### Stats
```{r}
stable_data<-read.csv(here::here("data/prob_err_by_phase_STABLES_contingency.csv"))
stable_data = assign_var_types(stable_data, c("trtype_str", "study_str", "id", "contingency", "ta"))

# estimate models
m1a<-lmer(prob ~ ta*contingency*trtype_str + (1|id) + (1|study_str), stable_data)
m1b<-lmer(prob ~ ta*contingency*trtype_str + (1|id) + (1+ta+contingency+trtype_str|study_str), stable_data)

# model comparison with and without random slope
anova(m1a, m1b)

# winning model overview
anova(m1a)

# marginals and post-hocs 
em1a1 = emmeans(m1a, specs = pairwise ~ trtype_str)
em1a1$emmeans
em1a1$contrasts

em1a2 = emmeans(m1a, specs = pairwise ~ trtype_str*contingency)
em1a2$emmeans
em1a2$contrasts

# trend with anxiety
emtrends(m1a, pairwise ~ trtype_str, var = "ta")

# one-way t-tests against true reinforcement (estimated by err)

df2 <- stable_data %>% 
    group_by(contingency, tabin, trtype_str) %>%
    nest() %>% 
    dplyr::mutate(tt=map(data,~t.test(.x$err))) %>%
    dplyr::mutate(tidied = map(tt, tidy)) %>% 
    unnest(tidied, .drop = T)

df2$p.value.fdr = p.adjust(df2$p.value, method = "fdr")

df2

## Gather model predictions and summarize for plots below 
stable_data$model_pred <- predict(m1a) 

```

### Plots
#### Stables 1: High/Low cue
```{r}
stable_data_df = stable_data %>%
  group_by(id, trtype_str) %>%
  summarise_at(c("model_pred","prob"), mean, na.rm = TRUE)


g <- ggplot(data = stable_data_df, aes(y = prob, x = trtype_str, fill = trtype_str)) +
geom_hline(yintercept = 0.75, color=pal[5], linetype="longdash")  +
geom_hline(yintercept = 0.25, color=pal[7], linetype="longdash")  +
  
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8, lwd=1.2) +
geom_point(aes(y = prob, color=trtype_str), position = position_jitter(width = .15), size = 2, alpha = 0.5, show.legend = FALSE) +
geom_boxplot(width = .2, outlier.shape = NA, alpha = 0.7, lwd=1.2, show.legend = FALSE) +
  

stat_summary(geom="point", fun="mean", size=4, shape=23,  stroke=1.5, aes(y=model_pred, group=trtype_str), color="black", show.legend = FALSE) +

expand_limits(x = 3) +

scale_color_manual(values = c(pal[5], pal[7])) +
scale_fill_manual(values = c(pal[5], pal[7]), name = "Stable cue", labels = c("High-prob Cue", "Low-prob Cue")) +  
# coord_flip() +
theme_bw() +
raincloud_theme +

theme(legend.position = "right") + 
labs(y= "Mean probability", x="Session") +
  scale_x_discrete(labels=c("hi-prob" = "HC", "low-prob" =  "LC")) + 
guides(fill=guide_legend(nrow=2,byrow=TRUE)) 

g
ggsave(here::here("output/figures/Fig_stable_1.pdf"), width = 6, height = 5, dpi = 120)
```
#### Stables 2: High/Low cue by session
```{r}
stable_data_df2 = stable_data  %>%
  group_by(id, trtype_str, contingency) %>%
  summarise_at(c("model_pred","prob"), mean, na.rm = TRUE)

w <- 0.4
g <- ggplot(data = stable_data_df2, aes(y = prob, x = contingency, fill = trtype_str))  
h<-c(0.6, 0.75, 0.9)
#
for (s in seq(3)) {
  g<- g + geom_segment(x=s-w,y=h[s], xend=s+w, yend=h[s] , linetype="dashed", color=pal[5], size=0.5 , alpha=0.3)
  g <- g + geom_segment(x=s-w,y=1-h[s], xend=s+w, yend=1-h[s] , linetype="dashed", color=pal[7], size=0.5 , alpha=0.3)
}
g<- g+geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8, show.legend = FALSE, lwd=1.2) +
geom_point(aes(y = prob, colour=trtype_str), position = position_jitterdodge(  jitter.width = .15,  dodge.width = 0.2), size = 2, alpha = 0.8, show.legend = FALSE) +
geom_boxplot(width = .2, outlier.shape = NA, alpha = 0.7,lwd=1.2, show.legend = FALSE) +
stat_summary(geom="point", fun="mean", size=4, shape=23, aes(y=model_pred, group=trtype_str), color="black", 
             position = position_dodge( 0.2), stroke=1.5, show.legend = FALSE) +
  
expand_limits(x = 3) +
scale_color_manual(values = c(pal[5], pal[7])) +
scale_fill_manual(values = c(pal[5], pal[7])) +  
theme_bw() +
raincloud_theme +
labs(y= "Mean probability", x="Session") +
guides(fill=guide_legend(nrow=2,byrow=TRUE)) 
g
ggsave(here::here("output/figures/Fig_stable_2.pdf"), width = 8, height = 5, dpi = 120)
```

#### Stables 3: High/Low cue by median-split TA
```{r}
stable_data_df3 = stable_data %>%
  group_by(id, trtype_str, tabin) %>%
  summarise_at(c("model_pred","prob"), mean, na.rm = TRUE)

g <- ggplot(data = stable_data_df3, aes(y = prob, x = trtype_str, fill = interaction(tabin,trtype_str))) +
geom_hline(yintercept = 0.75, color=pal[5], linetype="longdash")  +
geom_hline(yintercept = 0.25, color=pal[7], linetype="longdash")  +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8, lwd=1.2) +

geom_point(aes(color= interaction( tabin, trtype_str)), position =   position_jitterdodge(  jitter.width = .45,  dodge.width = 0.05), size = 2, alpha = 0.5, show.legend=FALSE) + 
geom_boxplot(width = .2, outlier.shape = NA, alpha = 0.7, lwd=1.2, show.legend = FALSE) +  
stat_summary(geom="point", fun="mean", size=4, shape=23, aes(y=model_pred, group=interaction(tabin,trtype_str)), color="black", 
             position = position_dodge( 0.2), stroke=1.5, show.legend = FALSE) +  
  
expand_limits(x = 3) +
scale_color_manual(values = c(pal[6], pal[5], pal[8], pal[7])) +
scale_fill_manual(values = c(pal[6], pal[5], pal[8], pal[7]), name = "", labels = c("HC: Low Anxiety", "HC: High Anxiety", "LC: Low Anxiety", "LC: High Anxiety")) +
theme_bw() +
raincloud_theme +
theme(legend.position = "right") + 
labs(y= "Mean probability", x="Session") +
  scale_x_discrete(labels=c("hi-prob" = "HC", "low-prob" =  "LC")) + 
guides(fill=guide_legend(nrow=4,byrow=TRUE)) 
g
ggsave(here::here("output/figures/Fig_stable_3.pdf"), width = 7, height = 5, dpi = 120)
```

#### Stables 4: Error from true by cue type, session and TA
```{r}
stable_data_df4 = stable_data %>%
  group_by(id, trtype_str, contingency, tabin) %>%
  summarise_at(c("model_pred", "err"), mean, na.rm = TRUE)

stable_data_df4 <- within(stable_data_df4, err[trtype_str=="hi-prob"] <- (err[trtype_str=="hi-prob"]))
# https://stackoverflow.com/questions/16026215/generate-ggplot2-boxplot-with-different-colours-for-multiple-groups
g <- ggplot(data = stable_data_df4, aes(y = err, x = trtype_str, fill = interaction( tabin, trtype_str))) +
geom_hline(yintercept=c(0), linetype="dashed") +
geom_point(aes(color= interaction( tabin, trtype_str)), position =   position_jitterdodge(  jitter.width = .45,  dodge.width = 1), 
           size = 2, alpha = 0.5, show.legend=FALSE) + 
geom_boxplot(inherit.aes = TRUE, width = 0.8, lwd=1.2, outlier.shape = NA, alpha = 0.7, show.legend = FALSE) +  
stat_summary(geom="point", fun="mean", size=4, shape=23, aes(y=err, group=interaction(tabin,trtype_str)), color="black", 
             position = position_dodge( 0.8), stroke=1.5, show.legend = FALSE) +
  
expand_limits(x = 3) +
scale_color_manual(values = c(pal[6], pal[5], pal[8], pal[7])) +
scale_fill_manual(values = c(pal[6], pal[5], pal[8], pal[7]), name = "", labels = c("HC: Low Anxiety", "HC: High Anxiety", "LC: Low Anxiety", "LC: High Anxiety")) +
theme_bw() +
raincloud_theme +
theme(legend.position = "right",
      strip.text.x = element_text(size = 12,  face = "bold"),
      strip.background = element_rect(color="black", fill="#ebebeb", size=0, linetype="solid")
      ) + 
labs(y= "Error", x="Session")  +
scale_x_discrete(labels=c("hi-prob" = "HC", "low-prob" =  "LC")) + 
ylim(-0.6, 0.6) +
facet_grid(cols=vars(contingency)) 
g
ggsave(here::here("output/figures/Fig_stable_4.pdf"), width = 8, height = 5, dpi = 120)
```

## 2. Analysis of ratings - reversal cue
### Stats
```{r}
rev_data<-read.csv(here::here("data/prob_err_by_phase_REV_contingency.csv"))
rev_data = assign_var_types(rev_data, c("phase_str", "study_str", "id", "contingency", "ta"))

m2a <-lmer(prob ~ ta*contingency*phase_str + (1|id)  + (1|study_str), rev_data) 
m2b<-lmer(prob ~ ta*contingency*phase_str + (1|id)  + (1+ta+contingency+phase_str|study_str), rev_data)
anova(m2a, m2b)

anova(m2a)

# post-hocs
em2a1 = emmeans(m2a, specs = pairwise ~ phase_str*contingency)
em2a1$emmeans
em2a1$contrasts

# relationship with anxiety
joint_tests(m2a, by = "phase_str")
emtrends(m2a, pairwise ~ phase_str, var = "ta")

# one-way t-tests against true reinforcement rates
df2 <- rev_data %>% 
    group_by(contingency, tabin, phase_str) %>%
    nest() %>% 
    mutate(tt=map(data,~t.test(.x$err))) %>%
    mutate(tidied = map(tt, tidy)) %>% 
    unnest(tidied, .drop = T)
df2$p.value.fdr = p.adjust(df2$p.value, method = "fdr")
df2$sig <- 0 
df2$sig[df2$p.value.fdr<0.05] <- 1
df2

# binarized anxiety to get means per group for descriptive tables (in supplementary)
m2c <-lmer(prob ~ tabin*contingency*phase_str + (1|id)  + (1|study_str), rev_data) 
em2c1 = emmeans(m2c, specs = pairwise ~ phase_str*tabin)
em2c1$emmeans

em2c2 = emmeans(m2c, specs = pairwise ~ phase_str*contingency*tabin)
em2c2$emmeans

em2c3 = emmeans(m2c, specs = pairwise ~ phase_str*contingency)
em2c3$emmeans
```

### Plots
#### reversal-locked ratings by state and anxiety
```{r}
rev_data_cont <- read.csv(here::here("data/chunked_data_byREV_only4viz.csv"))
rev_data_cont = assign_var_types(rev_data_cont, c("phase_str", "study_str", "id", "contingency", "ta", "half_str"))

#first summarize by participant
rev_data_cont_df = rev_data_cont %>%
  group_by(phase_str, contingency, id, trno) %>%
  summarise_at("prob", funs(mean),na.rm = TRUE)

df = rev_data_cont_df %>%
  group_by(phase_str, trno) %>%
  summarise_at("prob", funs(mean,std.error),na.rm = TRUE)
df$lower = df$mean - df$std.error
df$upper = df$mean + df$std.error

g <- ggplot(data = df, aes(y = mean, x = trno, fill=phase_str)) +
  geom_segment(x=0.5,y=0.75, xend=15, yend=0.75 , linetype="dashed", color=pal[1], size=0.5 , alpha=0.9) +
  geom_segment(x=0.5,y=0.25, xend=15, yend=0.25 , linetype="dashed", color=pal[3], size=0.5 , alpha=0.3) +
  geom_segment(x=-5,y=0.75, xend=-0.5, yend=0.75 , linetype="dashed", color=pal[3], size=0.5 , alpha=0.9) +
  geom_segment(x=-5,y=0.25, xend=-0.5, yend=0.25 , linetype="dashed", color=pal[1], size=0.5 , alpha=0.3) +
  
  geom_vline(xintercept=0, linetype="dashed") +
  geom_line(size=1.5, show.legend = TRUE) +
  geom_ribbon(aes(ymin=lower, ymax=upper),  na.rm = TRUE,alpha=0.8, show.legend = TRUE) + 
  geom_rect(xmin=10,xmax=15,ymin=0,ymax=1, size=2, color=pal2[7], fill=rgb(0.9, 0.9, 0.9), alpha=0.01) +
  scale_color_manual(values = c(pal[1], pal[3])) +
  scale_fill_manual(values = c(pal[1], pal[3]), name = "Switch type", labels = c("Low-to-high (L2H)", "High-to-low (H2L)")) +
  scale_x_continuous(breaks = c(-5, -1, 1, 5, 10, 15)) +
  ylim(0,1) + 
  theme_bw() +
  labs(y= "Rating", x="Trial (locked to reversal)")  +
  raincloud_theme  +
  theme(legend.position = c(0.35,0.9))
g
ggsave(here::here("output/figures/Fig_reversal_1.pdf"), width = 5, height = 5, dpi = 120)
```

#### reversal-locked ratings by state and anxiety
```{r}

#first summarize by participant
rev_data_cont_df2 = rev_data_cont %>%
  group_by(phase_str, tabin, contingency, id, trno) %>%
  summarise_at("prob", funs(mean),na.rm = TRUE)

df = rev_data_cont_df2 %>%
  group_by(phase_str,tabin, trno) %>%
  summarise_at("prob", funs(mean,std.error),na.rm = TRUE)
df$lower = df$mean - df$std.error
df$upper = df$mean + df$std.error


g <- ggplot(data = df, aes(y = mean, x = trno, fill=interaction(phase_str, tabin))) +
  geom_segment(x=0.5,y=0.75, xend=15, yend=0.75 , linetype="dashed", color=pal[1], size=0.5 , alpha=0.9) +
  geom_segment(x=0.5,y=0.25, xend=15, yend=0.25 , linetype="dashed", color=pal[3], size=0.5 , alpha=0.3) +
  geom_segment(x=-5,y=0.75, xend=-0.5, yend=0.75 , linetype="dashed", color=pal[3], size=0.5 , alpha=0.9) +
  geom_segment(x=-5,y=0.25, xend=-0.5, yend=0.25 , linetype="dashed", color=pal[1], size=0.5 , alpha=0.3) +
  geom_vline(xintercept=0, linetype="dashed") +
  geom_line(size=1.5, show.legend = TRUE) +
  geom_ribbon(aes(ymin=lower, ymax=upper),  na.rm = TRUE,alpha=0.6,show.legend = TRUE) + 
  scale_fill_manual(values = c(pal[2], pal[4], pal[1], pal[3]), name = "", labels = c("Low Anx: L2H", "Low Anx: H2L", "High Anx: L2H", "High Anx: H2L")) +
  scale_color_manual(values = c(pal[2], pal[4], pal[1], pal[3])) + 
  ylim(0,1) + 
  scale_x_continuous(breaks = c(-5, -1, 1, 5, 10), limits=c(-5,10)) +
  theme_bw() +
  labs(y= "Rating", x="Trial (locked to reversal)")  +
  raincloud_theme  +
  theme(legend.position = c(0.75,0.25))  
g
ggsave(here::here("output/figures/Fig_reversal_2.pdf"), width = 5, height = 5, dpi = 120)
```

#### reversal cue by anxiety, session and a state

```{r}
df = rev_data %>%
  group_by(id, phase_str, contingency, tabin) %>%
  summarise_at("prob", mean, na.rm = TRUE)

df_levs <- data.frame(contingency = c("60/40", "60/40", "75/25", "75/25", "90/10", "90/10"), 
                      phase_str = c("acq", "ext", "acq", "ext", "acq", "ext"),
                      level = c(60, 40, 75, 25, 90,10))
g <- ggplot(data = df, aes(y = prob, x = phase_str, fill = interaction( tabin, phase_str))) +
  geom_hline(data = df_levs[df_levs$phase_str == "acq",], aes(yintercept = level/100), color=pal[1], linetype="longdash", alpha =0.8) +
  geom_hline(data = df_levs[df_levs$phase_str == "ext",], aes(yintercept = level/100), color=pal[3], linetype="longdash", alpha =0.8) +
geom_point(aes(color= interaction( tabin, phase_str)), position =   position_jitterdodge(  jitter.width = .45,  dodge.width = 1), size = 2, alpha = 0.5, show.legend=FALSE) + 
geom_boxplot(inherit.aes = TRUE, width = 0.8, lwd=1.2, outlier.shape = NA, alpha = 0.7) + 
stat_summary(geom="point", fun="mean", size=4, shape=23, aes(group=interaction(tabin,phase_str)), color="black", 
             position = position_dodge( 0.8), stroke=1.5, show.legend = FALSE) +  
  
expand_limits(x = 3) +
scale_color_manual(values = c(pal[2], pal[1], pal[4], pal[3])) +
scale_fill_manual(values = c(pal[2], pal[1], pal[4], pal[3]), name = "", labels = c("HS: Low Anxiety", "HS: High Anxiety", "LS: Low Anxiety", "LS: High Anxiety")) +
theme_bw() +
raincloud_theme +
theme(strip.text.x = element_text(size = 14,  face = "bold"),
      strip.background = element_rect(color="black", fill="#ebebeb", size=0, linetype="solid")) +
theme(legend.position = "top") +  #c(0.8, 0.2)
labs(y= "Mean rating", x="State")  +
scale_x_discrete(labels=c("acq" = "High", "ext" =  "Low")) + 
facet_grid(cols=vars(contingency)) +
  guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
ylim(0,1)
g
ggsave(here::here("output/figures/Fig_reversal_3.pdf"), width = 10, height = 6, dpi = 120)

```

## 3. Analysis of slopes and switchpoints
### Stats
#### Slopes by anxiety and state
```{r}
rev_data <- read.csv(here::here("data/full_REV_data.csv"))

# We'll be fitting the slopes to the first ten trials after reversal
rev_data<-rev_data[which(rev_data$trno %in% seq(10)),]
rev_data = assign_var_types(rev_data, c("phase_str", "trno", "study_str", "id", "contingency", "ta", "half_str"))


# prepare data set
conts <- c("60/40", "75/25", "90/10")
phases <- c("acq", "ext") # acq= high-state; ext = low-state
halves <- c("first", "second")
df <- rev_data[,c("id", "ta")]
df<-df[!duplicated(df$id),]
df["tabin"]<-dicho(df$ta)
df$tabin <- mapvalues(df$tabin,
                           from = c(0,1),
                           to = c("lowAnx", "hiAnx"))
df["tabin"]<-to_factor(df["tabin"])

# run lmer for each combination of session, phase and half
dt <- data.frame()
for (c in conts) {
  for (ph in phases) {
    for (h in halves)  {
      adata <- rev_data[which((rev_data$phase_str %in% ph) & (rev_data$contingency %in% c) & (rev_data$half_str %in% h)),]
      mm = lmer(prob ~ 1 + (trno|id) , adata) # This estimates slope for each participant
      rn_a<- data.frame(ranef(mm))
      rn_a["id"] <- rn_a$grp
      df_a<-data.frame()
      df_a <- merge(df, rn_a[rn_a$term=="trno",], by="id")
      df_a["phase"] <- ph
      df_a["contingency"] <- c
      df_a["half"] <- h
      dt <- rbind(dt, df_a)
    }
  }
}
dt$phase_str = to_factor(dt$phase)
dt$contingency = to_factor(dt$contingency)
dt$half_str = to_factor(dt$half)
dt$abscondval <- abs(dt$condval)

# Also save the slope estiamtes for other anlayses
dt$slope <- dt$abscondval
write.csv(dt, here::here("data", "slope_estimates.csv"))

# Test on slopes (absolute slopes)
dfst<-read.csv(here::here("data/model_fit_final_full.csv"))
dfst<-dfst[,c("ids", "study", "contingency")]
dfst<-assign_var_types(dfst, c( "study", "ids")) 
dfst$id <- dfst$ids
dfst<-dfst[,c("study_str", "id", "contingency")]
dt <- base::merge(dt, dfst, by=c("id", "contingency"), all.x=TRUE)



# Report mean slopes using non-absolute values
m3b<-lmer(condval ~ ta*contingency*phase_str + (1|id) + (1|study_str), dt)
em3b = emmeans(m3b, specs = pairwise ~ phase_str)
em3b$emmeans

# main statistical model
m3a<-lmer(abscondval ~ ta*contingency*phase_str + (1|id) + (1|study_str), dt)
anova(m3a)

# m3a<-lmer(condval ~ ta*contingency*phase_str + (1|grp) , dt)
# anova(m3a)
# 
# # Post-hocs
em3a = emmeans(m3a, specs = pairwise ~ contingency)
em3a$emmeans
em3a$contrasts

joint_tests(m3a, by = "contingency")

# 
# # Interactions with trait anxiety
emtrends(m3a, pairwise ~ contingency, var = "ta")


```

#### slope and relative model fit
```{r}
fit_data <- read.csv(here::here("data/model_fit_final_full.csv"))
fit_data = assign_var_types(fit_data, c("contingency", "ta", "study", "ids"))
fit_data$id <- fit_data$ids
dt$slope <- abs(dt$condval)
dt2 = dt %>%
  group_by(id, contingency) %>%
  summarise_at(c("slope"), mean, na.rm = TRUE)

write.csv(dt2, here::here("../output", "tables_and_csvs", "est_slopes_1-10.csv"), row.names = FALSE)

df <- join(x=as.data.frame(dt2[,c("contingency", "slope", "id")]), y=as.data.frame(fit_data[, c("contingency", "id", "m1m3_diff", "ta")]), by=c("contingency", "id"))

### correlation between slope and relative model fit
df = df %>%
  group_by(id ) %>%
  summarise_at(c("slope", "m1m3_diff"), mean, na.rm = TRUE)
df<- as.data.frame(df)
cor.test(df$slope, df$m1m3_diff)

```

#### TODELETE: slope and relative model fit - regressing out baseline
```{r}
fit_data <- read.csv(here::here("data/model_fit_final_full.csv"))
fit_data = assign_var_types(fit_data, c("contingency", "ta", "study", "ids"))
fit_data$id <- fit_data$ids
dt$slope <- abs(dt$condval)

#### get baseline and regress it out
sdf<-read.csv(here::here("../output/full_behavioural_dataset_study_pX_real_data.csv"))
# Only reversal cue
sdf<-sdf[which(sdf$Trial_Type %in% 3),]
# Only trials just before reversal
sdf<-sdf[which(sdf$trno_onlypre %in% c(seq(-5, -1))),]
sdf<-sdf[which(sdf$rev_type_4plot %in% c("acq", "ext")),]
fields <- c("contingency","id", "rev_type_4plot")
sdf<- assign_var_types(sdf, fields)
sdf$phase_str <- sdf$rev_type_4plot
sdf = sdf %>%
  group_by(id, study_str,contingency, phase_str) %>%
  summarise_at("prob", mean, na.rm = TRUE)
sdf$baseline <- sdf$prob
baseline_df <- sdf
baseline_df$baseline <- baseline_df$prob

dtt <- base::merge(dt, baseline_df[,c("baseline", "id", "contingency", "phase_str")], by=c("id", "contingency", "phase_str"))


m<- lmer(data = dtt, slope ~ baseline + (1|phase_str/id) )
dtt$slope_regout <- resid(m)

dt2 = dtt %>%
  group_by(id, contingency) %>%
  summarise_at(c("slope_regout"), mean, na.rm = TRUE)



df <- join(x=as.data.frame(dt2[,c("contingency", "slope_regout", "id")]), y=as.data.frame(fit_data[, c("contingency", "id", "m1m3_diff", "ta")]), by=c("contingency", "id"))


### correlation between slope and relative model fit
df = df %>%
  group_by(id ) %>%
  summarise_at(c("slope_regout", "m1m3_diff"), mean, na.rm = TRUE)
df<- as.data.frame(df)
cor.test(df$slope_regout, df$m1m3_diff)

```

### Plots
#### Slopes by anxiety and state
```{r}



g <- ggplot(data = dt, aes(y = condval, x = phase, fill = interaction(tabin, phase_str))) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7,lwd=1.2) +
geom_point(aes(color= interaction( tabin, phase_str)), position = position_jitterdodge(  jitter.width = .15,  dodge.width = 0.2), size = 2, alpha = 0.5, show.legend=FALSE) + geom_boxplot(width = .2, outlier.shape = NA, alpha = 0.7, lwd=1.2, show.legend = FALSE) +
geom_hline(yintercept=c(0), linetype="dashed") +
stat_summary(geom="point", fun="mean", size=3, shape=23, aes(group=interaction(tabin,phase_str)), color="black", 
             position = position_dodge( 0.2), stroke=1, show.legend = FALSE) +    
  
  
expand_limits(x = 3) +
scale_color_manual(values = c(pal[2], pal[1], pal[4], pal[3])) +
scale_fill_manual(values = c(pal[2], pal[1], pal[4], pal[3]), name = "Trait anxiety", labels = c("Low", "High")) +
theme_bw() +
raincloud_theme +
theme(strip.text.x = element_text(size = 14,  face = "bold"),
    strip.background = element_rect(color="black", fill="#ebebeb", size=0, linetype="solid")) +
labs(y= "Slope on trials 1 - 10", x="State") + 
scale_x_discrete(labels=c("acq" = "High", "ext" =  "Low")) +
scale_y_continuous(labels = function(x) paste0(x*100, "%")) +
facet_grid(cols=vars(contingency)) 
g
ggsave(here::here("output/figures/Fig_slopes_1.pdf"), width = 10, height = 3, dpi = 120)
```

#### Correlation of TA and slope in 90/10 session

```{r}
### assumes previous dt

dt$slope <- abs(dt$condval)
dt2 = dt %>%
  group_by(id, contingency) %>%
  summarise_at(c("slope"), mean, na.rm = TRUE)

df <- join(x=as.data.frame(dt2[,c("contingency", "slope", "id")]), y=as.data.frame(fit_data[, c("contingency", "id", "m1m3_diff", "ta_orig_scale")]), by=c("contingency", "id"))

df<-df[df$contingency %in% "90/10",]
g <- ggplot(data = df, aes(x = ta_orig_scale, y = slope ), show.legend = FALSE) +
geom_point( ) +
geom_smooth(method='lm', formula= y~x, alpha=0.3, show.legend = FALSE, color="black") +
scale_color_gradient(low=pal[9], high=pal[9]) +
theme_bw() +
raincloud_theme +
  stat_cor(method = "pearson",  alternative = "two.sided",  cor.coef.name = c("r"),  label.sep = ", ",  label.x.npc = "left",  label.y.npc = "top", digits = 3, r.digits = 3, p.digits = 3) + 
  labs(x= "Trait anxiety", y="Slope on trials 1-10")   
g
ggsave(here::here("output/figures/Fig_slopes_2.pdf"), width = 5, height = 4, dpi = 120)

```

#### Switch steepness and switchpoint 

```{r}
stsw_data <- read.csv(here::here("data/steepness_and_switchpoint_full.csv"))
stsw_data = assign_var_types(stsw_data, c("study", "ta", "phase_str", "half_str", "cont", "tabin", "session"))

stsw_data = stsw_data %>%
  group_by(id, cont,phase_str, ta, study_str) %>%
  summarise_at(c("log_steepness", "steepness","switchpoint"), mean, na.rm = TRUE)

m <- lmer(log_steepness ~ ta*cont*phase_str + (1|id) + (1|study_str) , stsw_data)
anova(m)


col<- "slategray"
### Steepness plot
g <- ggplot(aes(x=cont, y=log_steepness, fill=cont), data=stsw_data) + 
  geom_flat_violin(position = position_nudge(x = .2, y = 0), lwd=1.2, alpha = .8, show.legend = FALSE) +
  geom_point(aes(y = log_steepness, color=cont), position = position_jitter(width = .15), size = 2, alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(width = .2, outlier.shape = NA, lwd=1.2,alpha = 0.7, show.legend = FALSE) + 
  stat_summary(geom="point", fun="mean", size=5, shape=23, aes(group=cont), color="black", 
             position = position_dodge( 0), stroke=1, show.legend = FALSE) + 
  expand_limits(x = 3) +
  scale_color_manual(values=c(col, col, col)) +
  scale_fill_manual(values=c(col, col, col)) +
  # coord_flip() +
  theme_bw() +
  raincloud_theme +
    labs(y= "Estimated (log) Steepness", x="Session") 
  g
ggsave(here::here("output/figures/Fig_steepness.pdf"), width = 5, height = 4, dpi = 120)


### Switchpoitn plot
col <- "slategray"
g <- ggplot(aes(x=cont, y=switchpoint, fill=cont), data=stsw_data) + 
  geom_flat_violin(position = position_nudge(x = .2, y = 0), lwd=1.2, alpha = .8, show.legend = FALSE) +
  geom_point(aes(y = switchpoint, color=cont), position = position_jitter(width = .15), size = 2, alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(width = .2, outlier.shape = NA, lwd=1.2, alpha = 0.7, show.legend = FALSE) +
  stat_summary(geom="point", fun="mean", size=5, shape=23, aes(group=cont), color="black", 
             position = position_dodge( 0), stroke=1, show.legend = FALSE) + 
  
  expand_limits(x = 3) +
  scale_color_manual(values=c(col, col, col)) +
  scale_fill_manual(values=c(col, col, col)) +
  theme_bw() +
  raincloud_theme +
  labs(y= "Estimated switch point", x="Session") 
  g
ggsave(here::here("output/figures/Fig_switchpoint.pdf"), width = 5, height = 4, dpi = 120)



```

## 4. Analysis of model fit and anxiety
### Stats
```{r}
fit_data <- read.csv(here::here("data/model_fit_final_full.csv"))
fit_data = assign_var_types(fit_data, c("study", "ta","contingency", "ids" ))

# m1m3_diff is relative model fit
m4a<-lmer(data=fit_data, m1m3_diff ~ ta*contingency + (1|ids) + (1|study_str))
anova(m4a)

# fit*correlation by session (p-vals uncorrected!)
joint_tests(m4a, by = "contingency")

# contrasts ta*fit effects between sessions (p-vals adjusted)
emtrends(m4a, pairwise ~ contingency, var = "ta")
```
### Plots

#### BIC scores (demeaned)
```{r}
df = fit_data %>%
  group_by(ids,contingency,ta) %>%
  summarise_at(c("m1_BIC","m3_BIC"), mean, na.rm = TRUE)

# Demean 
df <- df %>% gather(model, BIC, m1_BIC:m3_BIC)
dem_df <- df %>%
  group_by(contingency) %>%
  summarise_at(c("BIC"), mean, na.rm = TRUE)
dem_df$BICmean <- dem_df$BIC
dem_df$BIC <- NaN
df<- merge(x = df, y = dem_df, by = "contingency", all.x = TRUE)
df$BIC_demean <- df$BIC.x - df$BICmean

df_summ = df %>%
  group_by(model, contingency) %>%
  summarise_each(funs(mean,sd), BIC_demean)

g <- ggplot(df_summ, aes(x=model, y=mean, fill=model)) + 
          geom_bar(inherit.aes = TRUE, stat = "summary", color="black", show.legend = FALSE, width=0.8, lwd=1) + 
          scale_fill_manual(values = pal2[c(15,16)]) +
          scale_x_discrete(labels=c("1-state", "n-state")) +
          labs(y= "BIC (demeaned)", x="")  +
          facet_grid(~contingency) +
          
          theme_bw() +
          raincloud_theme 
g
ggsave(here::here("output/figures/Fig_model_comparison.pdf"), width = 5, height = 4, dpi = 120)
```

#### Relative model fit and anxiety in 90/10
```{r}

df <- fit_data[fit_data$contingency %in% c("90/10"),]
g <- ggplot(data = df, aes(x = m1m3_diff, y = ta, color=(m1m3_diff) )) +
geom_point( size = 5, alpha = 1, show.legend = FALSE) +
geom_smooth(method='lm', formula= y~x, alpha=0.3, show.legend = FALSE, color="black", fill="lightgray") +
scale_color_gradient2(low=pal2[15], midpoint = 0, mid = "grey39", high=pal2[16]) +
geom_vline(xintercept = 0, linetype = "longdash") +
theme_bw() +
stat_cor(method = "pearson",  alternative = "two.sided",  cor.coef.name = c("r"),  label.sep = ", ",  label.x.npc = "left",  label.y.npc = "top", digits = 3, r.digits = 3, p.digits = 3) + 
raincloud_theme +
labs(y= "Trait anxiety", x="Relative fit") 
g
ggsave(here::here("output/figures/Fig_model_fit_and_anxiety.pdf"), width = 7, height = 4.5, dpi = 120)
```
## 4b. Analysis of winning model parameters
### N-state
```{r}
data <- read.csv(here::here("data/models_no_states_and_switches_data.csv"))
 vars <- c("contingency", "ta", "study",  "ids")
 data <- assign_var_types(data, vars)
 df <- data %>% 
      melt(id.vars = c("ids", "ta", "study_str", "contingency"), measure.vars = c("tau_sh_reversalbsim", "tau_nosh_reversalbsim"), value.name = "tau", variable.name = "outcome" )
  df$outcome <- mapvalues(df$outcome,
                              from = c("tau_sh_reversalbsim", "tau_nosh_reversalbsim"),
                              to =c("sh", "nosh"))
  
  m <- lmer(data=df, tau ~ contingency*outcome*ta + (1|ids) + (1|study_str) )
 anova(m)
 memm <- emmeans(m, specs = pairwise ~ outcome)
 memm$emmeans
```
### 1-state
```{r}
data <- read.csv(here::here("data/models_no_states_and_switches_data.csv"))
vars <- c("contingency", "ta", "study",  "ids")
 data <- assign_var_types(data, vars)
 df <- data %>% 
      melt(id.vars = c("ids", "ta", "study_str", "contingency"), measure.vars = c("tau_sh_reversallbetav5", "tau_nosh_reversallbetav5"), value.name = "tau", variable.name = "outcome" )
  df$outcome <- mapvalues(df$outcome,
                              from = c("tau_sh_reversalbssm", "tau_nosh_reversalbssm"),
                              to =c("sh", "nosh"))
  
  m <- lmer(data=df, tau ~ contingency*outcome*ta + (1|ids) + (1|study_str) )
 anova(m)
 memm <- emmeans(m, specs = pairwise ~ outcome)
 memm$emmeans
 
 memm <- emmeans(m, specs = pairwise ~ outcome*contingency)
 memm$emmeans
```

## 5. Analysis of model-free learning rates from oddball and meaningful events
### Stats
#### Oddball/meaninful by anx and outcome
```{r}
# Load calcualted model-free learning rates
mflr_data <- read.csv(here::here("data/oddball_data_n5.csv"))
mflr_data = assign_var_types(mflr_data, c("study", "lrtype", "ta","contingency", "ids" ))
df <- melt(mflr_data, measure.vars=c("mflr_sh","mflr_nosh"),
    value.name = "mflr", variable.name="outcome_str")
df = assign_var_types(df, c("outcome_str" ))

m5a<-lmer(mflr ~ ta*contingency*lrtype*outcome_str + (1|ids) + (1|study_str), df)
anova(m5a)

# post hocs
em5a1 = emmeans(m5a, specs = pairwise ~ contingency:outcome_str)
em5a1$emmeans
em5a1$contrasts

em5a2 = emmeans(m5a, specs = pairwise ~ outcome_str)
em5a2$emmeans
em5a2$contrasts

# relationship with anxiety
emtrends(m5a, pairwise ~ lrtype, var = "ta")
```
#### Oddball/meaningful by best model per participant
```{r}
odd_model_data <- read.csv(here::here("data/oddball_by_model.csv"))
odd_model_data$best_model <- as.factor(odd_model_data$best_model)
t.test(mflr_diff~best_model, alternative = "two.sided", var.equal = FALSE, data=odd_model_data)

odd_model_data %>%
  group_by(best_model) %>%
  summarise_at(c("mflr_diff"), mean, na.rm = TRUE)




```

### Plots
#### Oddball/Meaninful by anxiety
```{r fig.width=4, fig.height=5}

df2 <- df %>%
  group_by(tabin, lrtype, ids, ta_orig_scale) %>%
  summarise_at(c("mflr"), mean, na.rm = TRUE)

dfnew <- df2 %>% tidyr::pivot_wider(
                  id_cols=c("ids", , "tabin", "ta_orig_scale"),
                  names_from=lrtype,
                  values_from=mflr 
                  ) 
dfnew$mflr_diff <- dfnew$common - dfnew$odd


g <- ggplot(data = dfnew, aes(y = mflr_diff, x = tabin, fill = tabin)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8, lwd=1.2, show.legend = TRUE) +
geom_point(aes(color= tabin), position =   position_jitterdodge(  jitter.width = .15,  dodge.width = 0.25), size = 2, alpha = 0.5, show.legend=FALSE) + 
geom_boxplot(width = .25, outlier.shape = NA, alpha = 0.7, lwd=1.2, show.legend = FALSE) +
stat_summary(geom="point", fun="mean", size=5, shape=23, aes(group=tabin), color="black", 
             position = position_dodge( 0.25), stroke=1, show.legend = FALSE) + 
expand_limits(x = 3) +
scale_color_manual(values = pal[c(2,1,2,4)] , name = "", labels = c("Low Anx", "High Anx")) +
scale_fill_manual(values = pal[c(2,1,2,4)], name = "", labels = c("Low Anx", "High Anx")) + 
theme_bw() +
raincloud_theme +
  theme(strip.text.x = element_text(size = 14,  face = "bold"),
      strip.background = element_rect(color="black", fill="#ebebeb", size=0, linetype="solid")) +
theme(legend.position = "top") + 
labs(y= "Meaningful-oddball learning difference", x="Trait anxiety") +
  scale_x_discrete(labels=c("Low", "High")) +
guides(fill=guide_legend(nrow=4,byrow=TRUE)) + 
  ylim(-0.1, 0.35)
g
ggsave(here::here("output/figures/Fig_oddball_anxiety.pdf"), width = 4, height = 5, dpi = 120)
```
#### Also plot continously
```{r fig.width=6, fig.height=5}

g <- ggplot(data = dfnew, aes(x = ta_orig_scale, y = mflr_diff, color=ta_orig_scale ), show.legend = FALSE) +
geom_point(size=3 ) +
geom_smooth(method='lm', formula= y~x, alpha=0.3, show.legend = FALSE, color="black") +
scale_color_gradient2(low=pal2[14], high=pal2[15], midpoint = 40, mid = pal2[13]) +
  #scale_color_gradient2(low=pal2[15], midpoint = 0, mid = "grey39", high=pal2[16]) +
theme_bw() +
raincloud_theme +
  stat_cor(method = "spearman",  alternative = "two.sided",  cor.coef.name = c("r"),  label.sep = ", ",  label.x.npc = "left",  label.y.npc = "top", digits = 3, r.digits = 3, p.digits = 3) + 
  
  labs(x= "Trait anxiety", y="Meaningful-oddball learning difference")   
g

ggsave(here::here("output/figures/Fig_oddball_anxiety_continuous.pdf"), width = 6.5, height = 5, dpi = 120)
```

```{r}
df2 <- df %>%
  group_by(contingency, tabin, lrtype, ids) %>%
  summarise_at(c("mflr"), mean, na.rm = TRUE)



g <- ggplot(data = df2, aes(y = mflr, x = tabin, fill = interaction(tabin, lrtype))) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8, lwd=1.2, show.legend = TRUE) +
geom_point(aes(color= interaction( tabin, lrtype)), position =   position_jitterdodge(  jitter.width = .15,  dodge.width = 0.25), size = 2, alpha = 0.5, show.legend=FALSE) + 
geom_boxplot(width = .2, outlier.shape = NA, alpha = 0.7, lwd=1.2, show.legend = FALSE) +
stat_summary(geom="point", fun="mean", size=5, shape=23, aes(group= interaction(tabin, lrtype)), color="black", 
             position = position_dodge( 0.25), stroke=1, show.legend = FALSE) + 
expand_limits(x = 3) +
scale_color_manual(values = pal[c(2,4,1,3,2,4)] ) +
scale_fill_manual(values = pal[c(2,4,1,3,2,4)]) + 
theme_bw() +
raincloud_theme +
theme(legend.position = "right") + 
labs(y= "Learning rate", x="") +
  scale_x_discrete(labels=c("common" = "Meaningful", "odd" =  "Oddball")) + 
guides(fill=guide_legend(nrow=4,byrow=TRUE)) 
g
```

#### Oddball/Meaninful by best fitted model
```{r fig.width=4, fig.height=5}
## Plot the difference as well
g <- ggplot(data = odd_model_data, aes(y = mflr_diff, x = best_model, fill =  best_model)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8, lwd=1.2) +
geom_point(aes(color= best_model), position =   position_jitterdodge(  jitter.width = .45,  dodge.width = 1), size = 2, alpha = 0.5, show.legend=FALSE) +  
geom_boxplot(inherit.aes = TRUE, width = 0.25, lwd=1.2, outlier.shape = NA, alpha = 0.7, show.legend = FALSE) + 
stat_summary(geom="point", fun="mean", size=5, shape=23, aes(group=best_model), color="black", 
             position = position_dodge( 1), stroke=1, show.legend = FALSE) + 
expand_limits(x = 3) +
scale_color_manual(values = c(pal2[15], pal2[16], pal[4], pal[3])) +
scale_fill_manual(values = c(pal2[15], pal2[16], pal[4], pal[3]), name = "", labels = c("1-state", "n-state")) +
theme_bw() +
raincloud_theme +
theme(strip.text.x = element_text(size = 14,  face = "bold"),
      strip.background = element_rect(color="black", fill="#ebebeb", size=0, linetype="solid")) +
theme(legend.position = "top") +  #c(0.8, 0.2)

labs(y= "Meaningful-oddball learning difference", x="Best model")  +

  guides(fill=guide_legend(nrow=1,byrow=TRUE)) +
ylim(-0.1, 0.35)
g

ggsave(here::here("output/figures/Fig_oddball_model.pdf"), width = 4, height = 5, dpi = 120)
```
```{r}
g <- ggplot(data = odd_model_data, aes(x = m1m3_diff, y = mflr_diff, color=m1m3_diff ), show.legend = FALSE) +
geom_point(size=3 ) +
geom_smooth(method='lm', formula= y~x, alpha=0.3, show.legend = FALSE, color="black") +
scale_color_gradient2(low=pal[3], high=pal[4], midpoint = -5, mid = pal[3]) +
  #scale_color_gradient2(low=pal2[15], midpoint = 0, mid = "grey39", high=pal2[16]) +
theme_bw() +
raincloud_theme +
  stat_cor(method = "kendall",  alternative = "two.sided",  cor.coef.name = c("r"),  label.sep = ", ",  label.x.npc = "left",  label.y.npc = "top", digits = 3, r.digits = 3, p.digits = 3) + 
  labs(x= "Model difference", y="Meaningful-oddball learning difference")   
g

ggsave(here::here("output/figures/Fig_oddball_model_continuous.pdf"), width = 6.5, height = 5, dpi = 120)

```
## 5 Additional figures and analyses
### Percentage participants by model 

```{r}

```


